Experimental and numerical studies of the effects of resonant and random excitations of the proton beam in the LHC, with applications to the design of a pulsed hollow electron lens for active halo control

### 2018-03-14 resex.tex
Revised text of 8th-turn results.

The small effect on the beam expected from simulations could then be
also confirmed experimentally during the 2017 experiment. For this
purpose the excitation amplitude was increased to the maximum
reachable amplitude of 96~nrad. As depicted in
Fig.~\ref{fig:8thexploss}, the loss rate increased slightly with the
excitation amplitude for an excitation in H+V. For an excitation only
in V or only in H, no statistically relevant increase was observed
(see Appendix~\ref{app:sec:8}, Fig.~\ref{fig:8thexploss2017}). In the
horizontal plane, a change in beam distribution was measured with the
BSRT profiles (Appendix~\ref{app:sec:8}, Fig.~\ref{fig:8thexpprof})
for an excitation only in~H. The distribution increased around
$2.0~\sigma$ simultaneously with a depletion of the beam core. For an
excitation in H+V one would expect to see a similar distribution
change. However, this change is not visible as the emittance of the
references bunches was much smaller, around $1.8~\mu$m normalized
emittance, compared to around $2.6~\mu$m for the excited bunches
\cite{resexmd2017}. This difference in emittance then resulted in a
stronger emittance growth due to intra-beam scattering for the
reference bunches in comparison to the excited bunches making the
additional emittance growth and distribution changes due to the
excitation undetectable. In the vertical plane, the beam distribution
and emittance were not affected by the resonant excitation.

% The small effect on the beam expected from simulations could then be
% also confirmed experimentally during the 2017 experiment. For this
% purpose the excitation amplitude was increased to the maximum
% reachable amplitude of 96~nrad. As depicted in
% Fig.~\ref{fig:8thexploss}, the loss rate increased slightly with the
% excitation amplitude for an excitation in H+V. For an excitation only
% in V or only in H, no statistically relevant increase was observed
% (see Appendix~\ref{app:sec:8}, Fig.~\ref{fig:8thexploss2017}). In the
% horizontal plane, a change in beam distribution was measured with the
% BSRT profiles (Appendix~\ref{app:sec:8}, Fig.~\ref{fig:8thexpprof})
% for an excitation only in~H. The distribution increased around
% $2.0~\sigma$ simultaneously with a depletion of the beam core. For an
% excitation in H+V one would expect to see a similar distribution
% change. However, this change is not visible as the emittance of the
% references bunches was much smaller, around $1.8~\mu$m normalized
% emittance, compared to around $2.6~\mu$m for the excited bunches
% \cite{resexmd2017}. This difference in emittance then resulted in a
% stronger emittance growth due to intra-beam scattering for the
% reference bunches in comparison to the excited bunches making the
% additional emittance growth and distribution changes due to the
% excitation undetectable. In the vertical plane, the beam distribution
% and emittance were not affected by the resonant excitation.

>>>>

The effects on the beam were tested during the 2017 experiment. The
excitation amplitude was increased to a maximum of 96~nrad. The loss
rates as a function of excitation amplitude are presented in
Fig.~\ref{fig:8thexploss2017}. For H and V excitations, no significant
increase of the loss rate was observed. A weak increase with amplitude
was seen in the case of H+V excitation. Observed and predicted loss
rates are of the same magnitude (about 0.2\%/h).

Changes in beam distributions were also detected
(Fig.~\ref{fig:8thexpprof}). The horizontal distribution responded to
the H excitation with a slight depletion of the core and a
corresponding increase around $2\sigma$. For an H+V excitation, one
would expect a similar distribution change. However, this change could
not be detected directly, because, in this case, the emittance of the
control bunches was much smaller (\q{1.8}{\mu m}) than the emittance
of the excited bunches (\q{2.6}{\mu m}), and intrabeam scattering
masked the effects of the excitation~\cite{resexmd2017}. In the
vertical plane, beam distributions and emittances were not affected
by the resonant excitation.
